---
title: '`r params$model@name@name`'
# author: ""
date: '`r format(Sys.Date(),"%Y-%B-%d")`'
output: word_document
params:
  model: NA
  plotCdf: NA
  plotTornado: NA
  plotHistogram: NA
  plotConvergence: NA
  plotUncertainties1: NA
  plotUncertainties2: NA
  plotUncertainties3: NA
---

\newpage

# Documentation

## Reference to the main document

`r params$model@basics@basics[[1]]@explanation`

## Background

`r params$model@basics@basics[[2]]@explanation`

## Objectives

`r params$model@basics@basics[[3]]@explanation`

## Scope

`r params$model@basics@basics[[4]]@explanation`

## Description

`r params$model@basics@basics[[5]]@explanation`

\newpage

# Authors
```{r authors, echo = FALSE}
#params$model@authors@authors
author_list <- NULL
for (author in params$model@authors@authors) {
  author_list <- paste(author_list, 
                       "Name:        ", author@name, "  \n", 
                       "Institution: ", author@institution, "  \n", 
                       "E-Mail:      ", author@email, "  \n\n")
}
```

`r author_list`

\newpage

# Definitions
```{r items, echo = FALSE}
params$model@items@items
```

\newpage

# Results

## Summary
```{r summary, echo = FALSE}
params$model@output@summaries
```

\newpage

## Plot CDF
```{r cdf, echo = FALSE, fig.cap = "CDF", out.width = "100%", fig.align = "center"}
if (file.exists(params$plotCdf))
  knitr::include_graphics(params$plotCdf)
```

\newpage

## Plot Tornado
```{r tornado, echo = FALSE, fig.cap = "Tornado", out.width = "100%", fig.align = "center"}
if (file.exists(params$plotTornado))
  knitr::include_graphics(params$plotTornado)
```

\newpage

## Plot Histogram
```{r histogram, echo = FALSE, fig.cap = "Histogram", out.width = "100%", fig.align = "center"}
if (file.exists(params$plotHistogram))
  knitr::include_graphics(params$plotHistogram)
```

\newpage

## Plot Convergence
```{r convergence, echo = FALSE, fig.cap = "Convergence", out.width = "100%", fig.align = "center"}
if (file.exists(params$plotConvergence))
  knitr::include_graphics(params$plotConvergence)
```

\newpage

## Plot Uncertainties
```{r uncertainties1, echo = FALSE, fig.cap = "Uncertainties", out.width = "100%", fig.align = "center"}
if (file.exists(params$plotUncertainties1))
  knitr::include_graphics(params$plotUncertainties1)
```

```{r uncertainties2, echo = FALSE, fig.cap = "Uncertainties", out.width = "100%", fig.align = "center"}
if (file.exists(params$plotUncertainties2))
  knitr::include_graphics(params$plotUncertainties2)
```

```{r uncertainties3, echo = FALSE, fig.cap = "Uncertainties", out.width = "100%", fig.align = "center"}
if (file.exists(params$plotUncertainties3))
  knitr::include_graphics(params$plotUncertainties3)
```